A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
Reword availability info

osf.io: The annotation as both a tab-separated values (TSV) formatted table and
TextGrid file as well as scripts and data of the analysis, doi:
\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}

>>>>

The annotation (tab-separated values (TSV) formatted table and TextGrid file),
as well as scripts and data of the validation analysis are available from
OpenScienceFramework project
\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}, and
accessible as DataLad (RRID:SCR\_003931) datasets.
